Geometrization of characters of tori over non-Archimedean local fields

### 2013-08-13 shanghai.tex
Fixed the home for boxtimes and re-named it to products.
But the proof that geochars on products are products of geochars is
still under construction

@@

The category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$},
is defined as follows.  A \cdef{geometrized character on $G$} is a triple
$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on  (the \'etale site of) $\bG$, locally constant of rank-$1$ on each connected component of $\bG$;
\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
%
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
  \end{tikzcd}
  \]

%
\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
%
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gcs{L} \arrow{rr}{\mu}
    && \LxL\\
  \end{tikzcd}
  \]
\end{enumerate}
Morphisms in $\GC(G)$ are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters of $G$ then
  $\Hom_{\GC(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
  \[
  \begin{tikzcd}[column sep=40]
  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
  & %\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
  & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \alpha} & m^* \gcs{L'} \dar{\mu'} \\
  \gcs{L} \rar{\alpha} & \gcs{L'}
  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
  \end{tikzcd}
  \]
\end{enumerate}

@@

\section{Boxproduct}

Let $ \GC(G_1) \boxtimes \GC(G_2)$

\begin{proposition}\label{prop:product}
The rule ... defines an equivalence of categories 
\[
\GC(G_1\times G_2) \to \GC(G_1) \boxtimes \GC(G_2)
\]
and 
\[
\begin{tikzcd}
\GCiso{G_1\times G_2} \arrow{r} & \GCiso{G_1} \times \GCiso{G_2}\\
(G_1\times G_2)(k)^* \arrow{r}  & G_1(k)^* \times G_2(K)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

@@

For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, we define a category of geometrized characters $\GC(G(\bFq))$.
An object in $\GC(G(\bFq))$ is given by the data of

\begin{enumerate}
 \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
  $G(\bFq)$;

@@

 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
    && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
    && \gcs{L}_x \otimes\gcs{L}_y
   \end{tikzcd}
  \]
  commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}

A morphism $\alpha : \cs{L} \to \cs{L'}$ is given by 
\begin{enumerate}
 \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
  of linear transformations (of one-dimensional $\EE$-vector spaces),
  as $x$ runs over $G(\bFq)$, such that
  \[
   \begin{tikzcd}[column sep=40]
    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes \alpha_y} & \gcs{L'}_x \otimes \gcs{L'}_y
   \end{tikzcd}
  \]
  both commute.
\end{enumerate}

>>>>

Also throughout the paper, $K$ is a non-Archimedean local field 
with residue field $\Fq$ and $T$ is an algebraic torus over $K$.

@@

A \cdef{geometrized character on $G$} is a triple
$\cs{L}\ceq (\gcs{L},\mu,\phi)$ where:
\begin{enumerate}
\labitem{(CS.0)}{CS.0} $\gcs{L}$ is a constructible $\ell$-adic sheaf on  (the \'etale site of) $\bG$, locally constant of rank-$1$ on each connected component of $\bG$;
\labitem{(CS.1)}{CS.1} $\mu: \bm^* \gcs{L} \to \LxL$
  is an isomorphism of sheaves on $\bGxG$ such that the following diagram commutes, 
  where $m_3 \ceq m\circ (m\tight{1}{\times}{2}\id) = m\circ (\id\tight{2}{\times}{1} m)$;
%
  \[
  \begin{tikzcd}[row sep=30]
  \bm_3^*\gcs{L} \arrow{rr}{(\bm \tight{1}{\times}{2} \id)^*\mu} \arrow[swap]{d}{(\id \tight{2}{\times}{1} \bm)^*\mu}
    &&  \bm^*\gcs{L} \boxtimes \gcs{L} \dar{\mu \tight{0}{\boxtimes}{1} \id} \\
    \gcs{L} \boxtimes \bm^* \gcs{L} \arrow{rr}{\id \boxtimes \mu}
    &&  \gcs{L} \tight{0}{\boxtimes}{0} \LxL\\
  \end{tikzcd}
  \]

%
\labitem{(CS.2)}{CS.2} $\phi : \Frob{G}^* \gcs{L} \to \gcs{L}$ is an
  isomorphism of constructible $\ell$-adic sheaves on $\bG$ compatible with $\mu$ in the sense that the following diagram commutes.
%
  \[
  \begin{tikzcd}[row sep=20]
  \Frob{\GxxG}^* \bm^* \gcs{L} \arrow{rr}{\Frob{\GxxG}^*\mu}
    && \Frob{\GxxG}^*(\LxL)\\
    \arrow[equal]{u} \bm^*  \Frob{G}^* \gcs{L} \arrow[swap]{d}{\bm^* \phi}
    && \Frob{G}^*\gcs{L}\boxtimes \Frob{G}^*\gcs{L} \dar{F\boxtimes \phi} \arrow[equal]{u} \\
    \bm^*\gcs{L} \arrow{rr}{\mu}
    && \LxL\\
  \end{tikzcd}
  \]
\end{enumerate}
Morphisms in the category of geometrized characters of $G$, denoted by \cdef{$\GC(G)$}, are defined in the natural way:
\begin{enumerate}
\labitem{(CS.3)}{CS.3} if $\cs{L} = (\gcs{L},\mu,\phi)$ and
  $\cs{L'} = (\gcs{L'},\mu',\phi')$ are geometrized characters of $G$ then
  $\Hom_{\GC(G)}(\cs{L},\cs{L'})$ is the set of morphisms $\alpha : \gcs{L} \to \gcs{L'}$
  of constructible $\ell$-adic sheaves on $\bG$ such that the following diagrams both commute.
  \[
  \begin{tikzcd}[column sep=40]
  \Frob{G}^* \gcs{L} \rar{\Frob{G}^* \alpha} \arrow[swap]{d}{\phi} & \Frob{G}^* \gcs{L'} \dar{\phi'}
  & %\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}} 
  & \arrow[swap]{d}{\mu} m^* \gcs{L} \rar{m^* \alpha} & m^* \gcs{L'} \dar{\mu'} \\
  \gcs{L} \rar{\alpha} & \gcs{L'}
  & {} & \LxL \rar{\tight{1}{\alpha\boxtimes \alpha}{1}} & \gcs{L'} \tight{0}{\boxtimes}{0} \gcs{L'}
  \end{tikzcd}
  \]
\end{enumerate}

@@

\section{Products}

\begin{proposition}\label{prop:product}
The rule $\boxtimes : (\cs{L}_1,\cs{L}_2)\to \cs{L}_1\boxtimes\cs{L}_2$ defines an equivalence of categories 
\[
\GC(G_1)\times(G_2) \to \GC(G_1\times G_2)
\]
and 
\[
\begin{tikzcd}[column sep=60]
\arrow{d}{t_{G_1} \times t_{G_2}} \GCiso{G_1}\times \GCiso{G_2} \arrow{r}{\boxtimes} & \arrow{d}{t_{G_1\times G_2}} \GCiso{G_1\times G_2}\\
(G_1)(\Fq)^*\times (G_2)(\Fq)^* \arrow{r}{(\chi_1,\chi_2)\mapsto \chi_1\otimes \chi_2}  & (G_1\times G_2)(\Fq)^*
\end{tikzcd}
\]
commutes.
\end{proposition}

\begin{proof}
\end{proof}

@@

For such a $\Gal(\bFq/\Fq)$-group $G(\bFq)$, 
\Clifton{Re-phrase.}
we define a category of geometrized characters $\GC(G(\bFq))$.
An object in $\GC(G(\bFq))$ is given by the data of
\begin{enumerate}
 \labitem{(cs.0)}{cs.0} an indexed set of one-dimensional
  $\EE$-vector spaces $\gcs{L}_x$, as $x$ runs over
  $G(\bFq)$;

@@

 \labitem{(cs.2)}{cs.2} an indexed set of isomorphisms $\phi_{x} : \gcs{L}_{\Frob{\Fq}(x)} \to \gcs{L}_x$
  such that
  \[
   \begin{tikzcd}[row sep=40]
    \gcs{L}_{\Frob{\Fq}(x)+\Frob{\Fq}(y)} \arrow[swap]{d}{\phi_{x+y}} \arrow{rr}{\mu_{\Frob{\Fq}(x),\Frob{\Fq}(y)}}
    && \gcs{L}_{\Frob{\Fq}(x)}\otimes \gcs{L}_{\Frob{\Fq}(y)} \dar{\phi_x \tight{0}{\otimes}{0} \phi_y} \\
    \gcs{L}_{x+y} \arrow{rr}{\mu_{x,y}}
    && \gcs{L}_x \otimes\gcs{L}_y
   \end{tikzcd}
  \]
  commutes, for all $x,y\in G(\bFq)$.
\end{enumerate}
A morphism $\alpha : \cs{L} \to \cs{L'}$ in $\GC(G(\bFq))$ is given by 
\begin{enumerate}
 \labitem{(cs.3)}{cs.3} an indexed set $\alpha_x : \gcs{L}_x \to \gcs{L'}_x$
  of linear transformations (of one-dimensional $\EE$-vector spaces),
  as $x$ runs over $G(\bFq)$, such that
  \[
   \begin{tikzcd}[column sep=40]
    \arrow[swap]{d}{\phi_x} \gcs{L}_{\Frob{\Fq}(x)} \rar{\alpha_{\Frob{\Fq}(x)}} & \gcs{L'}_{\Frob{\Fq}(x)} \dar{\phi_x'}
    &\arrow[draw=none]{d}[pos=.4,description]{\text{\normalsize{and}}}& \arrow[swap]{d}{\mu} \gcs{L}_{x+y} \rar{\alpha_{x+y}} & \gcs{L'}_{x+y} \dar{\mu'_{x+y}} \\
    \gcs{L}_x \rar{\alpha_x} & \gcs{L'}_x
    & {} & \gcs{L}_x\otimes\gcs{L}_y \rar{\alpha_x\otimes \alpha_y} & \gcs{L'}_x \otimes \gcs{L'}_y
   \end{tikzcd}
  \]
  both commute.
\end{enumerate}
